---
title: "Predicting SPAM with large logistic model"
author: "Mauricio G Tec"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Predicting SPAM with large logistic model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

To read our data we would use somethng like

```{r}
library(sparselogit)
library(readsvm) # install with devtools::install_github("SDS385team/readsvm")
```

```{r, eval = FALSE}
svm <- read_sparse_svm("D:/Datasets/full_url_svmlight.svm")
```

After reading it, we can store it as binary data for local purpose as

```{r, eval = FALSE}
res <- read_sparse_svm("D:/Datasets/full_url_svmlight.svm")
saveRDS(res, "D:/Datasets/full_url_svmlight.RDS")
```

And then read it faster with

```{r, eval = FALSE}
res <- readRDS("D:/Datasets/full_url_svmlight.RDS")
```

Since Support Vector Machine inputs the vector as -1,1 we should adjust

```{r, eval = FALSE}
y <- as.integer(res$response == 1)
table(y)
```

We can now run one pass (epoch) of our model like this (it runs in about 6.7 seconds):

```{r, eval = FALSE}
P <- nrow(res$features)
beta0 <- numeric(P)
system.time({
  mod <- sparse_logit(beta0, res$features, y, step_scale = 2, lambda = 1e-8, maxepochs = 1)
})
```

```{r, eval = FALSE}
save(beta0, mod, y, file = "Example.RData")
```

```{r, include = FALSE}
load("Example.Rdata")
```

We compare predictions and original data

```{r}
fitted_rounded <- round(mod$fitted)
table(y, fitted_rounded)
```
 
We have the following accuracy rate

```{r}
sum(y == fitted_rounded) / length(y)
```

We can sort and plot a few values of the coefficients

```{r}
plot(sort(sample(mod$coefficients, 10000)), type = "l", col = "blue", main = "Regression coefficients")
```

We can now run 10 epochs and see the improvment

```{r, eval = FALSE}
system.time({
  mod10 <- sparse_logit(beta0, res$features, y, step_scale = 2, lambda = 1e-8, maxepochs = 10)
})
```

```{r, eval = FALSE}
save(beta0, y, mod10, file = "Example2.RData")
```

```{r}
load("Example2.RData")
```

We compare predictions and original data

```{r}
fitted_rounded <- round(mod10$fitted)
table(y, fitted_rounded)
```
 
We have the following accuracy rate

```{r}
sum(y == fitted_rounded) / length(y)
```

We can sort and plot a few values of the coefficients

```{r}
plot(sort(sample(mod10$coefficients, 10000)), type = "l", col = "red", main = "Regression coefficients")
```

